**Results Template**

### 2021-09-16 scripts/claudia/data processing.Rmd
data extraction
deception task

```{r deception}

```

```{r merge all}
data_combined <- read.csv("demo.csv") %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q")))

>>>>

```{r deception subj}
rm(list=ls())
cat("\014")

mydata <- data.frame()
for (participant in list.files("../../data/data_experimental")) {
  df_sub <- read.csv(paste0("../../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), -c(5:34, 37:46, 48:54)]  
  mydata <- rbind(mydata, df_sub)
}

data <- mydata %>% 
  rename(item = V1,
       style = V2,
       condition = V3,
       question = V4,
       subresp = V35,
       RT = V36,
       ID = V47) %>%

  mutate(subresp = str_replace_all(subresp, "None", "0")) %>% 
  mutate(RT = str_replace_all(RT, "None", "0")) %>% 
  mutate(subresp = as.numeric(subresp)) %>% 
  mutate(RT = as.numeric(RT)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  mutate(ID = as.numeric(ID))

results <- data %>% 
  group_by(ID, condition, style) %>% 
  summarise(DT_SubjAvg = mean(subresp), DT_RTAvg = mean(RT)) %>% 
  group_by(ID, condition) %>% 
  mutate(DT_TotalAvg = mean(DT_SubjAvg), TotalRT = mean(DT_RTAvg)) %>% 
  rename(DT_condition = condition,
         DT_style = style)

write.csv(data, file = "deceptiontask_extracted.csv", row.names=FALSE)
write.csv(results, file = "deceptiontask_processed.csv", row.names=FALSE)
```

```{r merge all}
data_combined <- read.csv("demo.csv") %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains("Q"))) %>% 
  right_join(read.csv("deceptiontask_processed.csv"))
